Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach

### 2016-10-25 Multi-scale_Mobility_Pattern_CEUS/ijgi-148112-can be published.tex
temp

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{
The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
Junjun Yin would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{
The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
Junjun Yin, Yizhao Gao and Shaowen Wang would like to thank the funding support from the U.S. National Science Foundation under grant numbers: xx1, xx2, and xx3.
Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}
